Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Recovery, and Limits to Cosmology

### 2017-01-31 paper1.tex
only a single text change

A few caveats apply to the numbers given in Table \ref{tbl:mass bias} and Table \ref{tbl:mass scatter}. While we provide corrections for cluster masses above $10^{15}$ \msol, they are estimated from only a handful of objects owing to the volume in the mock galaxy catalog. These may not constitute a representative sample of clusters due to the limited volume and range of possible features. This becomes particularly apparent for the probability methods with many features. As the number of observed features increases, the number of training clusters in any particular bin decreases. This leads to highly skewed biases and scatters for the high mass clusters and probability methods. We do not report any bin where such small number statistics dominate in Tables~\ref{tbl:mass bias} and \ref{tbl:mass scatter}. On the opposite end of the cluster mass spectrum, there are very few, if any, clusters detected with Targeted or Survey observations below $5\times10^{12}$ \msol. Therefore, while we show these points in Figures~\ref{fig:Probability comparison} and \ref{fig: ML comparison}, we exclude their biases and scatters from Tables~\ref{tbl:mass bias} and \ref{tbl:mass scatter} for the same reasons.

>>>>

A few caveats apply to the numbers given in Table \ref{tbl:mass bias} and Table \ref{tbl:mass scatter}. While we provide corrections for cluster masses above $10^{15}$ \msol, they are estimated from only a handful of objects owing to the volume in the mock galaxy catalog. These may not constitute a representative sample of clusters due to the limited volume and range of possible features. This becomes particularly apparent for the probability methods with many features. As the number of observed features increases, the number of training clusters in any particular bin decreases. This leads to highly skewed biases and scatters for the high mass clusters and probability methods. We do not report biases and scatters (Tables~\ref{tbl:mass bias} and \ref{tbl:mass scatter}) of the Prob$_\sigma, z, N_gal$ method for high mass clusters because the predicted cluster masses are often based on $0-2$ training clusters. On the opposite end of the cluster mass spectrum, there are very few, if any, clusters detected with Targeted or Survey observations below $5\times10^{12}$ \msol. Therefore, while we show these points in Figures~\ref{fig:Probability comparison} and \ref{fig: ML comparison}, we exclude their biases and scatters from Tables~\ref{tbl:mass bias} and \ref{tbl:mass scatter} for the same reasons.
